ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-09-30 pyked.tex
Respond to #22
Add JSR and flow reactor experiments to the conclusion, and update the
Roadmap

\ck{} and \pk{} are currently under active development, and contributions from
the community are welcomed. All development occurs under the BSD 3-clause open source
license and the code is housed on GitHub at
\url{https://github.com/pr-omethe-us/PyKED}. Future directions for development
are outlined in the public
roadmap.\footnote{\url{https://github.com/pr-omethe-us/PyKED/wiki/Roadmap}}
The highest priority issues are currently adding support for other types of
fundamental experiments, including speciation in shock tubes, laminar flame speeds,
and flame extinction measurements.
Questions, comments, or suggestions are welcomed and can be posted as issues in the
GitHub repository or emailed to the authors. In particular, we welcome proposals for new
experimental types; see issue \#60 in the \pk{} repository for an example of how this may
be done.\footnote{\url{https://github.com/pr-omethe-us/PyKED/issues/60}}

>>>>

\ck{} and \pk{} are currently under active development, and contributions from the community are
welcomed. All development occurs under the BSD 3-clause open source license and the code is housed
on GitHub at \url{https://github.com/pr-omethe-us/PyKED}. Future directions for development are
outlined in the public roadmap.\footnote{\url{https://github.com/pr-omethe-us/PyKED/wiki/Roadmap}}
The highest priority issues are currently adding support for other types of fundamental experiments,
including speciation measurements in shock tubes, jet-stirred reactors, and flow reactors, and
laminar flame speed and flame extinction measurements. Questions, comments, or suggestions are
welcomed and can be posted as issues in the GitHub repository or emailed to the authors. In
particular, we welcome proposals for new experimental types; see issue \#60 in the \pk{} repository
for an example of how this may be
done.\footnote{\url{https://github.com/pr-omethe-us/PyKED/issues/60}}
